Effects of CHILDREN's programs

### 2020-02-26 paper.tex
ghj

% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Wed Feb 26 09:24:41 2020
\begin{table}[ht]
\centering
\begin{tabular}{mmmmm}
  \hline
Year & Beneficiaries, Meals & Beneficiaries, Trips & Organizations, Meals & Organizations, Trips \\ 
  \hline
2011 & 3748.0 &  & 52 &  \\ 
  2012 & 3556.0 & 2803.0 & 51 & 44 \\ 
  2013 & 4015.0 & 2823.0 & 55 & 42 \\ 
  2014 & 4685.0 & 2752.0 & 55 & 43 \\ 
  2015 & 5857.0 & 3823.0 & 55 & 49 \\ 
  2016 & 3075.0 & 3819.0 & 59 & 48 \\ 
  2017 & 4895.0 & 4150.0 & 64 & 48 \\ 
  2018 & 5102.5 & 6911.0 & 68 & 49 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{l c c c c c c }
\hline
 & MealsNo & Trips No & Meals No & Trips No & Meals No & Trips No \\
\hline
(Intercept)      & $-12089.14^{*}$ & $3.70^{***}$ & $-12089.14^{*}$ & $3.70^{***}$ & $-12250.60^{**}$ & $3.62^{***}$ \\
                 & $(5192.86)$     & $(0.33)$     & $(5192.86)$     & $(0.33)$     & $(4524.09)$      & $(0.33)$     \\
realSubsidy      & $2.61^{***}$    &              & $2.61^{***}$    &              & $2.72^{***}$     &              \\
                 & $(0.57)$        &              & $(0.57)$        &              & $(0.51)$         &              \\
realTripsSubsidy &                 & $0.00^{*}$   &                 & $0.00^{*}$   &                  & $0.00^{*}$   \\
                 &                 & $(0.00)$     &                 & $(0.00)$     &                  & $(0.00)$     \\
\hline
R$^2$            & 0.43            & 0.05         & 0.43            & 0.05         & 0.45             & 0.05         \\
Adj. R$^2$       & 0.43            & 0.04         & 0.43            & 0.04         & 0.45             & 0.05         \\
Num. obs.        & 329             & 322          & 329             & 322          & 440              & 334          \\
RMSE             & 39992.79        & 2.96         & 39992.79        & 2.96         & 39601.41         & 2.93         \\
\hline
\multicolumn{7}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
\caption{Grants Regressions}
\label{table:coefficients}
\end{center}
\end{table}

The first two columns are simple OLS models, in column 3 and 4 outliers are excluded and in column 5 and 6 data is imputed. 
(DESCRIBE RESULTS) (COMPARE TO SUMMARY STATISTICS)

@@

{\ttfamily\noindent\color{warningcolor}{\#\# Warning in gzfile(file, "{}rb"{}): kann komprimierte Datei './ANALYSIS/Tables/Expand\_LessIll\_IM\_scaled.Rds' nicht öffnen. Grund evtl. 'No such file or directory'}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): kann Verbindung nicht öffnen}}\end{kframe}
\begin{table}
\begin{center}
\begin{tabular}{l c c c c c c }
\hline
 & LessIll & DietaryKnowledge & AppreciateHealthy & LessIll & DietaryKnowledge & AppreciateHealthy \\
\hline
(Intercept)         & $0.02$       & $0.02$   & $-0.03$      & $0.09$       & $0.02$     & $0.02$       \\
                    & $(0.08)$     & $(0.07)$ & $(0.07)$     & $(0.07)$     & $(0.06)$   & $(0.06)$     \\
DGECriteriaNoScaled & $0.33^{***}$ & $0.11$   & $0.27^{***}$ & $0.25^{***}$ & $0.12^{*}$ & $0.25^{***}$ \\
                    & $(0.08)$     & $(0.06)$ & $(0.07)$     & $(0.07)$     & $(0.05)$   & $(0.06)$     \\
\hline
R$^2$               & 0.12         & 0.01     & 0.06         & 0.07         & 0.02       & 0.06         \\
Adj. R$^2$          & 0.11         & 0.01     & 0.06         & 0.07         & 0.01       & 0.06         \\
Num. obs.           & 121          & 214      & 213          & 177          & 275        & 274          \\
RMSE                & 0.91         & 0.98     & 1.02         & 0.94         & 0.96       & 1.01         \\
\hline
\multicolumn{7}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
\caption{Health Outcome Regressions}
\label{table:coefficients}
\end{center}
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{l c c c c c c c c }
\hline
 & selfworth & dayToDaySkills & selfworth & dayToDaySkills & selfworth & dayToDaySkills & selfworth & dayToDaySkills \\
\hline
(Intercept)      & $-13.42^{*}$ & $-13.48^{*}$ & $9.20^{***}$ & $8.25^{***}$ & $-0.06$  & $-0.16^{**}$ & $0.10$   & $0.12$   \\
                 & $(5.88)$     & $(5.89)$     & $(1.84)$     & $(1.78)$     & $(0.06)$ & $(0.06)$     & $(0.10)$ & $(0.11)$ \\
realSubsidy      & $0.00^{***}$ & $0.00^{***}$ &              &              & $0.00$   & $0.00^{***}$ &          &          \\
                 & $(0.00)$     & $(0.00)$     &              &              & $(0.00)$ & $(0.00)$     &          &          \\
realTripsSubsidy &              &              & $0.00^{***}$ & $0.01^{***}$ &          &              & $-0.00$  & $-0.00$  \\
                 &              &              & $(0.00)$     & $(0.00)$     &          &              & $(0.00)$ & $(0.00)$ \\
\hline
R$^2$            & 0.46         & 0.46         & 0.32         & 0.34         & 0.00     & 0.03         & 0.01     & 0.01     \\
Adj. R$^2$       & 0.45         & 0.45         & 0.31         & 0.34         & 0.00     & 0.03         & 0.00     & 0.01     \\
Num. obs.        & 428          & 426          & 184          & 177          & 430      & 428          & 186      & 178      \\
RMSE             & 41.50        & 41.59        & 21.93        & 21.36        & 1.00     & 0.98         & 1.00     & 0.98     \\
\hline
\multicolumn{9}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
\caption{Equal Opportunities Regressions}
\label{table:coefficients}
\end{center}
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{l c c c c c c c c }
\hline
 & selfworth & dayToDaySkills & selfworth & dayToDaySkills & selfworth & dayToDaySkills & selfworth & dayToDaySkills \\
\hline
(Intercept)      & $-13.42^{*}$ & $-13.47^{*}$ & $9.25^{***}$ & $8.33^{***}$ & $-0.06$  & $-0.16^{**}$ & $0.11$   & $0.13$   \\
                 & $(5.88)$     & $(5.89)$     & $(1.82)$     & $(1.74)$     & $(0.06)$ & $(0.06)$     & $(0.10)$ & $(0.11)$ \\
realSubsidy      & $0.00^{***}$ & $0.00^{***}$ &              &              & $0.00$   & $0.00^{***}$ &          &          \\
                 & $(0.00)$     & $(0.00)$     &              &              & $(0.00)$ & $(0.00)$     &          &          \\
realTripsSubsidy &              &              & $0.00^{***}$ & $0.00^{***}$ &          &              & $-0.00$  & $-0.00$  \\
                 &              &              & $(0.00)$     & $(0.00)$     &          &              & $(0.00)$ & $(0.00)$ \\
\hline
R$^2$            & 0.46         & 0.46         & 0.32         & 0.34         & 0.00     & 0.03         & 0.01     & 0.02     \\
Adj. R$^2$       & 0.45         & 0.45         & 0.31         & 0.34         & 0.00     & 0.03         & 0.01     & 0.01     \\
Num. obs.        & 428          & 427          & 186          & 180          & 430      & 429          & 189      & 182      \\
RMSE             & 41.50        & 41.54        & 21.83        & 21.21        & 1.00     & 0.98         & 1.00     & 0.99     \\
\hline
\multicolumn{9}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
\caption{Equal Opportunities Regressions, imputed data}
\label{table:coefficients}
\end{center}
\end{table}

@@

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mi, Feb 26, 2020 - 09:24:46
% Requires LaTeX packages: dcolumn rotating 
\begin{sidewaystable}[!htbp] \centering 
  \caption{Regression Results} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
\hline \\[-1.8ex] 
 Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
  & (0.065) & (0.095) & (0.092) & (0.107) \\ 
  & & & & \\ 
 treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
  & (0.074) & (0.097) & (0.075) & (0.100) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
ID fixed effects & No & No & Yes & Yes \\ 
Time fixed effects & No & Yes & No & Yes \\ 
Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{sidewaystable}

@@

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mi, Feb 26, 2020 - 09:24:46
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Less Ill} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -2.799 & 1.109 & -2.523 & 0.012 \\ 
\multicolumn{1}{c}{(Intercept):2} & 1.653 & 0.582 & 2.841 & 0.004 \\ 
\multicolumn{1}{c}{(Intercept):3} & 4.667 & 0.738 & 6.322 & 0 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.291 & 0.075 & -3.883 & 0.0001 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mi, Feb 26, 2020 - 09:24:46
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Dietary Knowledge} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -4.009 & 0.803 & -4.996 & 0.00000 \\ 
\multicolumn{1}{c}{(Intercept):2} & -1.047 & 0.425 & -2.465 & 0.014 \\ 
\multicolumn{1}{c}{(Intercept):3} & 1.445 & 0.430 & 3.365 & 0.001 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.089 & 0.052 & -1.712 & 0.087 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mi, Feb 26, 2020 - 09:24:46
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Appreciate Healthy} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -1.603 & 0.486 & -3.298 & 0.001 \\ 
\multicolumn{1}{c}{(Intercept):2} & 0.586 & 0.413 & 1.419 & 0.156 \\ 
\multicolumn{1}{c}{(Intercept):3} & 3.052 & 0.471 & 6.483 & 0 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.199 & 0.053 & -3.744 & 0.0002 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mi, Feb 26, 2020 - 09:24:46
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Equality of opportunities, selfworth} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -4.855 & 0.584 & -8.315 & 0 \\ 
\multicolumn{1}{c}{(Intercept):2} & -1.268 & 0.143 & -8.893 & 0 \\ 
\multicolumn{1}{c}{(Intercept):3} & 1.514 & 0.150 & 10.109 & 0 \\ 
\multicolumn{1}{c}{realSubsidy} & -0.00001 & 0.00001 & -1.332 & 0.183 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

>>>>

% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Wed Feb 26 12:29:41 2020
\begin{table}[ht]
\centering
\begin{tabular}{mmmmm}
  \hline
Year & Beneficiaries, Meals & Beneficiaries, Trips & Organizations, Meals & Organizations, Trips \\ 
  \hline
2011 & 3748.0 &  & 52 &  \\ 
  2012 & 3556.0 & 2803.0 & 51 & 44 \\ 
  2013 & 4015.0 & 2823.0 & 55 & 42 \\ 
  2014 & 4685.0 & 2752.0 & 55 & 43 \\ 
  2015 & 5857.0 & 3823.0 & 55 & 49 \\ 
  2016 & 3075.0 & 3819.0 & 59 & 48 \\ 
  2017 & 4895.0 & 4150.0 & 64 & 48 \\ 
  2018 & 5102.5 & 6911.0 & 68 & 49 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\end{table}

@@

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c }
\hline
 & OLS & OLS without Outliers & OLS Impute \\
\hline
(Intercept) & $-12089.14^{*}$ & $-12089.14^{*}$ & $-12250.60^{**}$ \\
            & $(5192.86)$     & $(5192.86)$     & $(4524.09)$      \\
realSubsidy & $2.61^{***}$    & $2.61^{***}$    & $2.72^{***}$     \\
            & $(0.57)$        & $(0.57)$        & $(0.51)$         \\
\hline
R$^2$       & 0.43            & 0.43            & 0.45             \\
Adj. R$^2$  & 0.43            & 0.43            & 0.45             \\
Num. obs.   & 329             & 329             & 440              \\
RMSE        & 39992.79        & 39992.79        & 39601.41         \\
\hline
\multicolumn{4}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Number of meals}
\label{table:coefficients}
\end{center}
\end{table}

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c }
\hline
 & OLS & OLS without Outliers & OLS Impute \\
\hline
(Intercept)      & $3.70^{***}$ & $3.70^{***}$ & $3.62^{***}$ \\
                 & $(0.33)$     & $(0.33)$     & $(0.33)$     \\
realTripsSubsidy & $0.00^{*}$   & $0.00^{*}$   & $0.00^{*}$   \\
                 & $(0.00)$     & $(0.00)$     & $(0.00)$     \\
\hline
R$^2$            & 0.05         & 0.05         & 0.05         \\
Adj. R$^2$       & 0.04         & 0.04         & 0.05         \\
Num. obs.        & 322          & 322          & 334          \\
RMSE             & 2.96         & 2.96         & 2.93         \\
\hline
\multicolumn{4}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Number of trips}
\label{table:coefficients}
\end{center}
\end{table}

@@

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & OLS & WLS & OLS Impute & WLS Impute \\
\hline
(Intercept)         & $0.02$       & $0.46^{**}$ & $0.09$       & $0.39^{***}$ \\
                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.12)$     \\
DGECriteriaNoScaled & $0.33^{***}$ & $0.35^{*}$  & $0.25^{***}$ & $0.24$       \\
                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.14)$     \\
\hline
R$^2$               & 0.12         & 0.29        & 0.07         & 0.16         \\
Adj. R$^2$          & 0.11         & 0.29        & 0.07         & 0.16         \\
Num. obs.           & 121          & 120         & 177          & 177          \\
RMSE                & 0.91         & 7.83        & 0.94         & 7.95         \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Less Ill}
\label{table:coefficients}
\end{center}
\end{table}

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & OLS & WLS & OLS Impute & WLS Impute \\
\hline
(Intercept)         & $0.02$   & $0.08$   & $0.02$     & $0.21$   \\
                    & $(0.07)$ & $(0.19)$ & $(0.06)$   & $(0.18)$ \\
DGECriteriaNoScaled & $0.11$   & $-0.02$  & $0.12^{*}$ & $0.10$   \\
                    & $(0.06)$ & $(0.12)$ & $(0.05)$   & $(0.14)$ \\
\hline
R$^2$               & 0.01     & 0.00     & 0.02       & 0.01     \\
Adj. R$^2$          & 0.01     & -0.00    & 0.01       & 0.01     \\
Num. obs.           & 214      & 212      & 275        & 275      \\
RMSE                & 0.98     & 8.49     & 0.96       & 9.45     \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Dietary Knowledge}
\label{table:coefficients}
\end{center}
\end{table}

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & OLS & WLS & OLS Impute & WLS Impute \\
\hline
(Intercept)         & $-0.03$      & $0.26$   & $0.02$       & $0.37^{*}$ \\
                    & $(0.07)$     & $(0.18)$ & $(0.06)$     & $(0.17)$   \\
DGECriteriaNoScaled & $0.27^{***}$ & $-0.02$  & $0.25^{***}$ & $0.01$     \\
                    & $(0.07)$     & $(0.15)$ & $(0.06)$     & $(0.13)$   \\
\hline
R$^2$               & 0.06         & 0.00     & 0.06         & 0.00       \\
Adj. R$^2$          & 0.06         & -0.00    & 0.06         & -0.00      \\
Num. obs.           & 213          & 211      & 274          & 274        \\
RMSE                & 1.02         & 8.61     & 1.01         & 9.00       \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Appreciate Healthy}
\label{table:coefficients}
\end{center}
\end{table}

@@

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & OLS Lunch & OLS Trips & OLS Lunch Impute & OLS Trips Impute \\
\hline
(Intercept)                    & $0.08$   & $0.12$   & $0.09$   & $0.12$   \\
                               & $(0.09)$ & $(0.12)$ & $(0.09)$ & $(0.11)$ \\
realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          \\
                               & $(0.00)$ &          & $(0.00)$ &          \\
realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  \\
                               &          & $(0.00)$ &          & $(0.00)$ \\
\hline
R$^2$                          & 0.00     & 0.01     & 0.00     & 0.01     \\
Adj. R$^2$                     & 0.00     & 0.01     & 0.00     & 0.01     \\
Num. obs.                      & 428      & 184      & 430      & 187      \\
RMSE                           & 1.00     & 1.00     & 1.00     & 1.00     \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Selfworth}
\label{table:coefficients}
\end{center}
\end{table}

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & OLS Lunch & OLS Trips & OLS Lunch Impute & OLS Trips Impute \\
\hline
(Intercept)                    & $0.15$   & $0.13$   & $0.14$   & $0.11$   \\
                               & $(0.09)$ & $(0.10)$ & $(0.09)$ & $(0.10)$ \\
realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          \\
                               & $(0.00)$ &          & $(0.00)$ &          \\
realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  \\
                               &          & $(0.00)$ &          & $(0.00)$ \\
\hline
R$^2$                          & 0.01     & 0.01     & 0.01     & 0.01     \\
Adj. R$^2$                     & 0.01     & 0.01     & 0.01     & 0.01     \\
Num. obs.                      & 426      & 177      & 429      & 181      \\
RMSE                           & 1.00     & 0.98     & 1.00     & 0.99     \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: dayToDaySkills}
\label{table:coefficients}
\end{center}
\end{table}

@@

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mi, Feb 26, 2020 - 12:29:46
% Requires LaTeX packages: dcolumn rotating 
\begin{sidewaystable}[!htbp] \centering 
  \caption{Regression Results} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
\hline \\[-1.8ex] 
 Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
  & (0.065) & (0.095) & (0.092) & (0.107) \\ 
  & & & & \\ 
 treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
  & (0.074) & (0.097) & (0.075) & (0.100) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
ID fixed effects & No & No & Yes & Yes \\ 
Time fixed effects & No & Yes & No & Yes \\ 
Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{sidewaystable}

@@

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mi, Feb 26, 2020 - 12:29:47
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Less Ill} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -2.799 & 1.109 & -2.523 & 0.012 \\ 
\multicolumn{1}{c}{(Intercept):2} & 1.653 & 0.582 & 2.841 & 0.004 \\ 
\multicolumn{1}{c}{(Intercept):3} & 4.667 & 0.738 & 6.322 & 0 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.291 & 0.075 & -3.883 & 0.0001 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mi, Feb 26, 2020 - 12:29:47
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Dietary Knowledge} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -4.009 & 0.803 & -4.996 & 0.00000 \\ 
\multicolumn{1}{c}{(Intercept):2} & -1.047 & 0.425 & -2.465 & 0.014 \\ 
\multicolumn{1}{c}{(Intercept):3} & 1.445 & 0.430 & 3.365 & 0.001 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.089 & 0.052 & -1.712 & 0.087 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mi, Feb 26, 2020 - 12:29:47
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Appreciate Healthy} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -1.603 & 0.486 & -3.298 & 0.001 \\ 
\multicolumn{1}{c}{(Intercept):2} & 0.586 & 0.413 & 1.419 & 0.156 \\ 
\multicolumn{1}{c}{(Intercept):3} & 3.052 & 0.471 & 6.483 & 0 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.199 & 0.053 & -3.744 & 0.0002 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mi, Feb 26, 2020 - 12:29:47
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Equality of opportunities, selfworth} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -4.855 & 0.584 & -8.315 & 0 \\ 
\multicolumn{1}{c}{(Intercept):2} & -1.268 & 0.143 & -8.893 & 0 \\ 
\multicolumn{1}{c}{(Intercept):3} & 1.514 & 0.150 & 10.109 & 0 \\ 
\multicolumn{1}{c}{realSubsidy} & -0.00001 & 0.00001 & -1.332 & 0.183 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}
